The pollination trade-off

### 2018-08-26 paper/supp-info.Rmd
Figure of correlation between explanatory variables
Close #17
Make figure all results larger

```{r fig-model-results, fig.height = 3.5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain. Only results for the models with the most parsimonous fixed effects. "}
drake::readd(fig_all_model_results)
```

>>>>

```{r fig-correlation, fig.height = 4.5, fig.cap = "Corelation between the explanatory variables included in the statistical models."}
drake::readd(fig_correlation)
```

```{r fig-model-results, fig.height = 7, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain. Only results for the models with the most parsimonous fixed effects. "}
drake::readd(fig_all_model_results)
```
